---
title: "Day 4 Interactive Session"
format: html
editor: visual
---

```{r}
library(tidyverse)
```

## Functions

a function that doubles a value

```{r}
double_value <- function(my_dollars) {
  print(2 * my_dollars)
}
#nothing returned yet because this is just making the function
```

```{r}
double_value(my_dollars = 10.13)
```

```{r}
#you don't need to specify the varaible
double_value(10.13)
```

```{r}
monthly_income <- c(42.50, 61.75, 89.50)
double_value(monthly_income)
```

Making a function that returns an awesome restaurant name given a cool animal and your favorite food.

```{r}
#pasting string and printing it
name_restaurant <- function(animal, food) {
  print(paste0(animal, food))
}

name_restaurant(animal="hawk", food= "pizza")
```

Given temperature in degrees Fahrenheit, write a function that coverts it to Celsius.

```{r}
temp_celsius <- function(temp_F) {
  print((temp_F -32)*(5/9))
}

temp_celsius(temp_F = 32)
```

Make a function that given inputs of age and hometown returns i am \_\_\_ and i'm from \_\_\_\_

```{r}
introduction_fn <- function(age, hometown){
  print(paste0("I am ",age," years old, and I'm from ", hometown, "."))
}

introduction_fn(age= 22, hometown = "Buena Park")
```

```{r}
double_value2 <- function(dollars){
  dollars * 2
}
double_value2(dollars = 10)
```

## Functions with conditionals

```{r}
calculate_animal_age <- function(species, age_human_years) {
  if (species == "dog"){
    age_human_years * 7
  } else if(species =="goat"){
    age_human_years * 4.7
  } else (
    print("Please enter dog or goat.")
  )
}

calculate_animal_age(species ="dog", age_human_years = 10)
calculate_animal_age(species = "goat", age_human_years = 4)

#what happens if i use calculate animal is whale? nothing happens
calculate_animal_age(species = "whale", age_human_years = 10)
#not evaluated if it doesn't mean the condition 
```

Write a function that, given temperature in Kelvin, if a user selects "metric" to the scale then return degrees Celsius, or if they select "english" then return degrees in Fahrenheit.

```{r}
# two arguments, input of temp in kelvin; and user selection of metric or english

kelvin_conversion <- function(scale, temp_k){
  if (scale =="metric")(
    temp_k-273.15
  )else if (scale == "english")(
    ((temp_k- 273.15) *1.8) +32
  ) else
    print('Please enter metric or english.')
}

kelvin_conversion(scale= "metric", temp_k = 40)
```

```{r}
# Build & check the minimum function
logistic_growth <- function(N0, K, r, time) {
  Nt <- K / (1 + ((K - N0) / N0) * exp(-r * time))
  print(Nt)
}

# Do the values check out when you test this? 
logistic_growth(N0 = 100, K = 6000, r = 0.27, time = 40)
```

## More functions

making a data frame and function will return a single row, like making a subset within a function

Make a subset within a function , and then return something based on that subset

```{r}
dog_choice <- data.frame(dog_name= c("Khora","Teddy","Waffle","Banjo","Tallie"),
                                 food =c("everything",
                                           "salmon","pancakes","chicken","enchiladas"))
```

```{r}
dog_menu <- function(enter_dog_name){
  selected_dog <- filter(dog_choice, dog_name == enter_dog_name)
  print(paste("My name is", selected_dog$dog_name, "and my favorite food is",
              selected_dog$food))
}
dog_menu("Khora")
#given some dog name, subset only stores one row and we will pull information from that existing row, filtering a function , filtering data frame to single row. 

#selected_dog is only keeping row in dog_choice data frame if dog name user enters matches. filter statement asks if it matches the name in each of the row, the only thing kept is the one row. 
```

## Function with a for loop 

```{r}
# if all the variables are numeric, then tell all the means. iterate from 1 to number of columns is in that data frame
df_means <- function(df){
  for (i in seq_along(df)){
    col_mean <- mean(df[[i]], na.rm = TRUE)
    column_name <- colnames(df[i])
    print(paste("The mean value of", column_name, "is", col_mean))
  }
}
```

```{r}
df_means(df = mtcars)
```

```{r}
df_means(faithful)
```
